\chapter{Audience, Platform, and Marketing}

\section{Target audience}% 3.1 Target audience
\urgent[inline]{Who will buy your game? Describe the demographic you are targeting, including age, gender, and geographic locations.}

El público objetivo de este videojuego está conformado por aquellas personas que
tienen preferencia por los juegos de plataformas y desean jugar partidas rápidas
casuales con amigos sin necesidad de mucha configuración previa. Algunas
características adicionales de las personas de esta audiencia son:

\begin{itemize}
    \item No desean jugar algo demasiado técnico o complejo.
    \item Tendrán una edad igual o mayor a 7 años, tomando en cuenta que el
    juego contendrá violencia caricaturesca e insultos no vulgares.
    \item No se espera que se identifiquen con ningún género en específico. No se considera que el género
    vaya a ser un factor importante a la hora de seleccionar el juego.
    \item Serán de habla hispana. El juego será principalmente desarrollado en
    castellano, por lo que el público principal serán personas de habla hispana.
\end{itemize}

\section{Platform} % 3.2 Platform
\urgent[inline]{What platform or platforms will your game run on? Why did you choose these platforms?}

\section{System requirements} % 3.3 System requirements
\urgent[inline]{System requirements might limit your audience, especially on the PC or mobile phones, where the hardware varies widely. Describe what is required to play the game and why those choices were made.}

\section{Top performers} % 3.4 Top performers
\urgent[inline]{List other top-selling games in the same market. Provide sales figures, release dates, information on sequels and platforms, as well as brief descriptions of each title.}

\section{Feature comparison} % 3.5 Feature comparison
\urgent[inline]{Compare your game to the competition. Why would a consumer purchase your game over the others?}

\section{Sales expectations} % 3.6 Sales expectations
\urgent[inline]{Provide an estimate of sales over the first year broken down by quarter. How many units will be sold globally, as well as within key markets, like the United States, England, Japan, etc.?}
